---
title: "Iteration"
author: Amanda Warnock
output: github_document
---


```{r}
library(tidyverse)
library(rvest)
```

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```
I want a function to compute z scores. 

```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  return(z)
  
}

z_scores(x_vec)
```

try my function on some other things.

```{r, error = TRUE}
z_scores(3)
```
^NA

```{r, error = TRUE}
z_scores("my name is amanda")
```
^error

```{r, error = TRUE}
z_scores(iris)
```
^cant coerce to type double 

```{r, error = TRUE}
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```
^coerces it, still wrong though

update function to make it break if used wrong

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}
```

check that it works
```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_and_sd(x_vec)
```

## multiple inputs 

```{r}
sim_data = tibble(
  x = rnorm(n = 100, mean = 4, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```
id like to do this ^ w/ a function

```{r}
sim_mean_sd = function(n, mu, sigma) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

sim_mean_sd(100, 6, 3)
sim_mean_sd(mu = 6, n = 100, sigma = 3)
```
(mu and sigma bc true pop parameters)
(this is positional matching, named matching can also be used and generally should be)
if you set the originals to numbers, they will be overridden during matching if you specify it 


## revisit nap dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

```

what about the next page of reviews though? time to turn into function.

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

reviews =   
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```
try  it

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```
can remove global environment by restarting r to make sure that its reading in just what you want it to

## mean scoping example

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)

```
got 4 bc of how r does scoping --> goes searching for y and finds it in the global environment bc its not in the function

## function as arguments

```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)
```



